---
title: "DSCI 301 - MidTerm"
author: "Put your name"
date: "Oct 04, 2019"
output: html_document
---

Part one:
Load the dat2.csv file into R and name it “tips”. Based on this dataset, answer the following questions.

```{r}
tips <- read.csv("dat2.csv")
```


1. Display the first 10 rows of the dataset tips.(4pts)

```{r}
head(tips, 10)
#Or another solution
tips[1:10, ]
```


2. For the dataset tips, filter records of female customers who have total bill greater than or equal to 20.(7pts)

```{r}
subset(tips, sex == "Female" & total_bill >= 20)
```


3. Add a new variable called tip_percentage by calculating the ratio of tip to total_bill.(7pts)

```{r}
#You will need dplyr function to use the mutate function
library(dplyr)
tips <- mutate(tips, tip_percentage = tip / total_bill)

#Or 

tips$tip_percentage <- tips$tip / tips$total_bill



```



4. Plot a scatterplot of the tip_percentage by total bill size.(7pts)

```{r}
library(ggplot2)
ggplot(data = tips, mapping = aes(x = total_bill, y = tip_percentage)) +
  geom_point()

```



5. Change the color of the scatterplot in #4 into blue.(7pts)

```{r}

ggplot(data = tips, mapping = aes(x = total_bill, y = tip_percentage)) +
  geom_point(color = "blue")

```


6. Have the color of the scatterplot in #4 vary by the variable smoker.(7pts)

```{r}

ggplot(data = tips, mapping = aes(x = total_bill, y = tip_percentage)) +
  geom_point(aes(color = smoker))

#Or

ggplot(data = tips, mapping = aes(x = total_bill, y = tip_percentage, color = smoker)) +
  geom_point()

```


7. Have the color of the scatterplot in #4 vary by the variables smoker and time.(7pts)
At the exam I updated the wording: have the scatterplot vary by smoker and time.

```{r}
ggplot(data = tips, mapping = aes(x = total_bill, y = tip_percentage)) +
  geom_point() +facet_grid(smoker ~ time)
```


8. Add a suitable title, x-axis and y-axis.(4pts)

```{r}
# It didn't specify to which graph, I accepted if you added title and axes to the another graphs (not graph #8).

ggplot(data = tips, mapping = aes(x = total_bill, y = tip_percentage)) +
  geom_point() +facet_grid(smoker ~ time) +
  labs(title = "Add a title here",
       x = "Add x-axis name ",
       y = "Add y-axis name ")

```




Part Two:

Load the starwars.csv file into R and name it “starwars”. Based on this dataset, answer the following
questions.

```{r}
starwars <- read.csv("starwars.csv")

```


1. Give a summary of the dataset starwars. (3pts)

```{r}
summary(starwars)
```



2. Plot a bar chart by gender for the data set starwars.(6pts)

```{r}
ggplot(data = starwars, mapping = aes(x = gender)) +
  geom_bar()
```


3. Plot a bar chart (count) by gender for the data set starwars, and give them a gray70 color.(6pts)

```{r}
ggplot(data = starwars, mapping = aes(x = gender)) +
  geom_bar(fill = "gray70")
```

4. Plot a bar chart (proprtions) by gender for the data set starwars, and give them a gray70 color.
(7pts)

```{r}
ggplot(data = starwars, mapping = aes(x = gender)) +
  geom_bar(aes(y = ..prop.., group = 1))

#Or

ggplot(data = starwars, mapping = aes(x = gender, y = ..prop.., group = 1)) +
  geom_bar()


```


5. Plot a stacked bar chart for gender by hair_color.(7pts)

```{r}
ggplot(data = starwars, mapping = aes(x = gender, fill = hair_color)) +
  geom_bar()

```



6. For each gender, set the bars of the variable hair_color side-by-side.(7pts)

```{r}
ggplot(data = starwars, mapping = aes(x = gender, fill = hair_color)) +
  geom_bar(position = "dodge")

```


7. Repeat #6 above but change y- axis to show proportions.(7pts)

```{r}
ggplot(data = starwars, mapping = aes(x = gender, y = ..prop.., group = hair_color, fill = hair_color)) +
  geom_bar(position = "dodge")

```


8. Facet wrap #6 above by hair_color, and adjust the width so that you can read the x-axis labels.
(7pts)


```{r}
ggplot(data = starwars, mapping = aes(x = gender, fill = hair_color)) +
  geom_bar(position = "dodge") +
  facet_wrap(~hair_color)

```




